Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-07-10 Journal1/Response3/Response.tex

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the Editor for his comments and concluding the revisions on our manuscript and for giving us this opportunity to improve our paper. We have used the comments to improve our paper and eliminate problems.

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The authors have addressed the comments provided in a previous review. The contributions are clear and the results are compared to some related work, so the reader can somewhat contextualize the proposed solution. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``However, the paper still needs some improvement in terms of readability. Some paragraphs are too long  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We revised the whole paper and checked the text entirely according to this comment.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` the figures are difficult to locate from their reference in the text (figures at top, as typical IEEE template is better), the text in the figures is too small ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for this comment. We modified all the paper's figures entirely concerning this comment.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``the contributions discussed in the introduction are not easily found in the other parts of the paper.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We thank the reviewer for adding clarity to our paper and reducing ambiguity in this condition.  We changed the contribution in a better way based on this comment. We have removed some sentences and rewritten the contribution in order to our paper's section.
Below we write the whole contribution section.

This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
\item We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
\end{itemize}

@@

% % % % % % % % % % % % % % % Reviewer 2 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 2} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The Reviewer would like to thank the authors for their revision of the paper with respect to the comments and suggestions in the previous submission. Whereas the authors have considered parts of the suggestions and improved specific areas of the work, there are still a lot of remaining issues of concern in the current version of the paper. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing
thoughtful comments, and offering constructive suggestions that strengthened and enhanced its
quality. We hope that the responses provided herein can alleviate the reviewer’s concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``While the authors have taken into consideration the Reviewer’s comments about the re-structuring of the Introduction, I am afraid that the current version is not in the adequate state for publication. Initially, the paragraphs of the Introduction have no logical connection among them. It seems that until the Related Literature subsection all paragraphs are disconnected and only introduce concepts. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable. 
We modified the introduction completely and add it below

\section{Introduction}
%\subsection{State Of The Arts}
Network slicing is a key technology in 5G wireless systems. Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes [1]–[3]. There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming. Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity. Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads  [4]–[6].
%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}

@@

Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig. 1, is introduced to deal with these issues.
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container [7].
As a result, some O-RAN components defined in Section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.

\subsection{Motivation}
The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2], [8], [9].

Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service. Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient. In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost. Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges. 
One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1], [10]–[12].  
%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation. Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.

\subsection{Main Contributions}

This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
\item We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.
\item We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
\end{itemize}

Table I lists the acronyms used throughout this paper, which is organized as follows.
Relevant literature related to our work is discussed in Section II, while Section III briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section IV, V, respectively. The details of our proposed resource management algorithm are introduced in Section VI. In Section VII, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section VIII concludes the paper.

 \vspace*{-2em}
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary. I would definitely suggest to move that as a background Section. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I would appreciate your comments to enhance and clarify this section of the paper. I moved the background as a section and modified it even as follow.

O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence. O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN). With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly. The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool [27]. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
 Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.

In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN. As shown in Fig. 1, O-RU is a logical node that contains RF and low PHY. The former transmits or receives radio signals, while the latter includes digital beamforming. Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC. It contains a subfunction of the eNodeB and is deployed near the O-RU.
Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).
O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. Orchestration and Automation include functions such as RIC Non-Real-Time. RIC is responsible for machine learning methods and making the system more intelligent  [10]–[12], [28]–[31].
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} `` Furthermore, it is surprising how the Introduction does not contain a single research challenge. Why is the problem relevant at all? Why do you even need to study this problem and why is it hard to solve? ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We added the motivation subsection and answer these questions in it.

The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2], [8], [9].

Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service. Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient. In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost. Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges. 
One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1], [10]–[12].  
%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

@@

The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation. Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment4:} `` In turn, in the main contributions subsection, the initial sentences of almost all contribution paragraphs cannot be considered as contributions. For instance:

1) “We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.”
2) “ Different services need to consider varying QoS conditions, including delay, power, and throughput.”
3) “The main problem is mixed-integer non-linear programming that is extremely difficult to solve.”
''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We removed these sentences and rewrite the main contribution. Below we present the modified main contribution.

### 2022-07-10 Journal1/paper5TNSM/pr.tex
add latex

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.36]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}

@@

Table \ref{table:11a} lists the acronyms used throughout this paper, which is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.

@@

  VM & virtual machine  \\[.5ex]
  RAN &  radio access network \\[.5ex]
 O-RAN & open RAN  \\[.5ex]
 vRAN & virtual RAN \\[.5ex]
 CRAN & cloud RAN \\[.5ex]
   QoS &  quality of service \\[.5ex]
  MIMO & multiple input multiple output \\[.5ex]
  PRB &  physical resource block \\[.5ex]

  eMBB & enhanced mobile broadBand \\[.5ex]

@@

\section{Background}\label{BG}
\textcolor{MidnightBlue}{O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence. O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).} With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly. The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
\textcolor{MidnightBlue}{ Most real-time baseband processing is performed in the O-DU layer, while mostly non-real-time baseband processing is executed in the O-CU layer. Therefore, the three-layer O-RAN architecture can achieve lower cost and power consumption benefits than the two-layer C-RAN architecture.}

As shown in Fig. \ref{fig:c11}, O-RU is a logical node that contains RF and low PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
%\begin{table}[H]
% \caption {List OF Notation} \label{table:1a}
% \begin{center}
% \scalebox{0.8}{
%  \begin{tabular}{||c | c ||}
%  \hline
%Notation & Description \\ [0.5ex]
%  \hline\hline
%  $S$ & Total number of slices\\
%  \hline
%  $S1$ & Number of eMBB slices  \\
%  \hline
% $S2$ & Number of URLLC slices  \\
%  \hline
%  $S3$ & Number of mMTC slices \\
%  \hline
%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
%  \hline
%  PRB &  Physical Resource Block \\
%  \hline
%  eMBB & enhanced Mobile BroadBand \\
%  \hline
%  URLLC  & Ultra-Reliable Low Latency Communication \\
%   \hline
%  mMTC &  massive Machine-To-Machine Communications \\
%  \hline
%  O-RU &  O-RAN Radio Unit \\
%  \hline
%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
%  \hline
%   O-CU &  O-RAN Central Unit \\ [.5ex]
%  \hline
%  UPF &  User Plane Function \\ [.5ex]
%  \hline
% \end{tabular}}
% \end{center}
% \end{table}
\section{System Model and Problem Formulation}\label{systemmodel}
We consider a downlink (DL) , and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
In this section, we present the system model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system. Moreover, we discuss the mean delay and the power of VNFs, and formulate the main problem under consideration.
\subsection{System Model}
Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S = S_1 + S_2 + S_3$ pre-allocated slices serving these services.
Moreover, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have the set
$\{1,2,...,S_1\}$ of eMBB service instances, the set $\{1,2,...,S_2\}$ of URLLC service instances, and the set
$\{1,2,...,S_3\}$ of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
Based on the application and QoS request, UE may be admitted and allocated to the resources.

Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item MAC/RLC functions in the O-DU logical node
\item PDCP/SDAP functions in the O-CU-UP logical node
\item UPF logical node
\end{itemize}
Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP, and $M_s^{u}$ VNFs for the processing of UPF.
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, which is defined as the service function chain in the O-RAN system. Also, each VNF instance runs on a virtual machine VM that uses resources from the data centers.

@@

This paper aims to maximize the sum-rate of all UEs with the presence of constraints as follows. %{\color{red} where did you define the objective? what is R bar?}

@@

&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\

@@

&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\

@@

& \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r, \label{c18-1} \\
& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r, \label{c18} \\
& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i. \label{c21}

@@

\noindent where $\bar{\mathcal{R}}_{u_{(s,i)}}, \:\:\forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.

>>>>

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.36]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipment (UE). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}

@@

Table \ref{table:11a} lists the acronyms used throughout this paper, which is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}, \ref{prS}, respectively. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.

@@

  VM & virtual machine  \\[.5ex]
  RAN &  radio access network \\[.5ex]
 O-RAN & open RAN  \\[.5ex]
 vRAN & virtual RAN \\[.5ex]
 CRAN & cloud RAN \\[.5ex]
   QoS &  quality of service \\[.5ex]
  MIMO & multiple input multiple output \\[.5ex]
  PRB &  physical resource block \\[.5ex]
  SINR & signal to interference and noise ratio  \\[.5ex]
  eMBB & enhanced mobile broadBand \\[.5ex]

@@

\section{Background}\label{BG}
\textcolor{MidnightBlue}{O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexibility, openness, low operational costs, and intelligence. O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).} With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly. The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
\textcolor{MidnightBlue}{ Most real-time baseband processing is performed in the O-DU layer, while non-real-time baseband processing is mostly executed in the O-CU layer.}

\textcolor{MidnightBlue}{In the O-RAN architecture, the PHY is divided into low and high PHY, unlike C-RAN. As shown in Fig. \ref{fig:c11}, O-RU is a logical node that contains RF and low PHY. The former transmits or receives radio signals, while the latter includes digital beamforming. Typically, the O-DU constitutes a logical node with high PHY, MAC, and RLC. It contains a subfunction of the eNodeB and is deployed near the O-RU.
Moreover, O-DU is connected to an O-RU with an open fronthaul interface.
In addition to supporting the lower layers of the protocol stack, O-CU also provides support for the higher layers.
The O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). The former hosts the packet data convergence protocol (PDCP)-UP and the service data adaption protocol (SDAP), while the latter hosts PDCP-CP and radio resource control (RRC).}
O-DU and O-CU are connected via an open and well-defined interface $\text{F}_1$.
The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. \textcolor{MidnightBlue}{Orchestration and Automation include functions such as RIC Non-Real-Time. RIC is responsible for machine learning methods and making the system more intelligent}
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
%\begin{table}[H]
% \caption {List OF Notation} \label{table:1a}
% \begin{center}
% \scalebox{0.8}{
%  \begin{tabular}{||c | c ||}
%  \hline
%Notation & Description \\ [0.5ex]
%  \hline\hline
%  $S$ & Total number of slices\\
%  \hline
%  $S1$ & Number of eMBB slices  \\
%  \hline
% $S2$ & Number of URLLC slices  \\
%  \hline
%  $S3$ & Number of mMTC slices \\
%  \hline
%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
%  \hline
%  PRB &  Physical Resource Block \\
%  \hline
%  eMBB & enhanced Mobile BroadBand \\
%  \hline
%  URLLC  & Ultra-Reliable Low Latency Communication \\
%   \hline
%  mMTC &  massive Machine-To-Machine Communications \\
%  \hline
%  O-RU &  O-RAN Radio Unit \\
%  \hline
%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
%  \hline
%   O-CU &  O-RAN Central Unit \\ [.5ex]
%  \hline
%  UPF &  User Plane Function \\ [.5ex]
%  \hline
% \end{tabular}}
% \end{center}
% \end{table}
\section{System Model}\label{systemmodel}
We consider a downlink (DL) system, and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
In this section, we present the system and signal model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system. Moreover, we discuss the mean delay and the power of VNFs.
\subsection{System Model}
Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S = S_1 + S_2 + S_3$ pre-allocated slices serving these services.
Moreover, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have the set
$\{1,2,...,S_1\}$ of eMBB service instances, the set $\{1,2,...,S_2\}$ of URLLC service instances, and the set
$\{1,2,...,S_3\}$ of mMTC service instances.
Each service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
Based on the application and QoS request, UE may be admitted and allocated to the resources.

Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item MAC/RLC functions in the O-DU 
\item PDCP/SDAP functions in the O-CU-UP
\item UPF which is a functional layer
\end{itemize}
Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP, and $M_s^{u}$ VNFs for the processing of UPF.
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, which is defined as the service function chain in the O-RAN system. Also, each VNF instance runs on a VM that uses resources from the data centers.

@@

This paper aims to maximize the sum-rate of all UEs subject to QoS constraints as follows. %{\color{red} where did you define the objective? what is R bar?}

@@

&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i, r, s, k,\label{c12} \\
&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i, r, s, k,\label{c12-1} \\

@@

&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i, s,\label{c16} \\

@@

& \bar{\mathcal{R}}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i, s,\label{c16-2} \\

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s, i, \label{c17}  \\
& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s, i , r, \label{c18-1} \\
& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s, i , r, \label{c18} \\
& g^r_{u(s,i)} \in \{0,1\} \quad \forall s, i, \label{c20}  \\
& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s, i. \label{c21}

@@

\noindent \noindent where $\bar{\mathcal{R}}_{u_{(s,i)}}$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
In addition, $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , i, r, k $, is the four-dimensional (4D) matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , i, r, k$ indicates the binary 4D matrix for the PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , i, r$ is a binary three dimensional (3D) matrix for the O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is a matrix containing the number of VNFs in each layer of slice. Notice that 
